\documentclass{article}
\title{Notes Section 1} % title
\author{John Yang}
\usepackage{amsmath}
\usepackage[margin=1in, letterpaper]{geometry}
\usepackage{outlines}
\setcounter{section}{6} % chapter number minus 1
\usepackage{mathtools}
\DeclarePairedDelimiter\set\{\}
\usepackage{hyperref}
\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	filecolor=magenta,      
	urlcolor=cyan,
}
\usepackage{tocloft}
\renewcommand\cftsecfont{\normalfont}
\renewcommand\cftsecpagefont{\normalfont}
\renewcommand{\cftsecleader}{\cftdotfill{\cftsecdotsep}}
\renewcommand\cftsecdotsep{\cftdot}
\renewcommand\cftsubsecdotsep{\cftdot}

\begin{document}
    \maketitle
    \tableofcontents
    \section{Reflections on my trip(s) to various cities}
    \subsection{Atlanta}
    \begin{outline}
        \1 Basic Information
            \2 \textbf{When} did I go?
                \3 11/4/2021 (Thursday)
            \2 \textbf{Who} did I go with? Who did I meet/already know there?
                \3 Traveled alone, but met up with Emily Hang at GT. 
            \2 \textbf{Why} did I go? (What was the purpose of my trip?)
                \3 College visit for Georgia Tech. 
            \2 \textbf{What} did I do there?
                \3 Flew into ATL. Had breakfast at Sun In My Belly restaurant. Went on a campus tour at GT. Visited Centennial Olympic Park, National Center for Civil and Human Rights. Walked around GT with Emily, then went back to ATL. 
            \2 \textbf{Where} did I go, if it wasn't mentioned already?
                \3 I also kinda walked around some of the residential areas around GT, as well as near the restaurant in Oakhurst. 
                \3 Tried to go to the Delta Flight Museum but it was closed. 
        \1 Impressions
            \2 People: 
                \3 There were a lot of anti-maskers at GT, which was interesting. GT doesn't have a mask mandate because the University System of Georgia won't allow them to. 
                \3 People were pretty nice overall. How do I even judge the niceness of people?
            \2 Transit:
                \3 I mainly took the MARTA subway to places, and I didn't really use the bus. 
            \2 Climate:
                \3 The weather was really bad that day - it was cold and rainy for most of the morning, but that's apparently as bad as it gets in Georgia. 
            \2 Perceptions of the city's planning:
                \3 The thing I was really annoyed about is how there's a literal interstate that runs through the center of the city. Many cities have rivers that separate different geographical locations. Atlanta doesn't have that, but they somehow decided to do it artificially by building a damn highway right through the middle of the city?? Make it make sense. 

            \2 External POVs:
        \1 Other information 
            \2 Historical context:
                \3 Obviously, the South had a lot of segregation and the effects have inertia. 
            \2 Additional notes 
                \3 Whenever I visit a new city, if I have time, I like to try to go to the non-touristy areas to get a better sense of what the city is like. In Atlanta, I sort of achieved this by going to that breakfast restaurant that was not close to downtown at all. However, I could tell that I was in a probably more affluent neighborhood. 
            \2 Final thoughts
                \3 I really enjoyed my time in Atlanta, even though I was only there for a day and the weather was kinda nasty in the morning. Being able to ride local transit and go beyond the typical tourist attractions is always valuable to me, and I appreciated the glimpse into Atlanta's communities. I certainly did not get the sense at any point that it was unsafe or dangerous. 

    \end{outline}
    \subsection{Baltimore}
    \begin{outline}
        \1 Basic Information
            \2 \textbf{When} did I go?
                \3 11/5/2021 (Friday)
            \2 \textbf{Who} did I go with? Who did I meet/already know there?
                \3 I was travelling alone, and I didn't really have people I knew in Baltimore except for my old coworker Charlotte, who I briefly met for a drink. 
            \2 \textbf{Why} did I go? (What was the purpose of my trip?)
                \3 I was visiting Johns Hopkins University. 
            \2 \textbf{What} did I do there?
                \3 Arrived late at night, chilled in the airport until the morning, where I then had breakfast at the Blue Moon Cafe. Then, I had my tour at JHU; had lunch at Bird in Hand Coffee, visited the Baltimore Museum of Art, had some boba with Charlotte, then moved on to DC. 
            \2 \textbf{Where} did I go, if it wasn't mentioned already?
                \3 I spent a really long time in Penn Station bcs I didn't want to leave at 10 PM, also what was I even going to do at that hour anyway?
        \1 Impressions
            \2 People: The people were very nice. There seemed to be a good amount of diversity too. 
            \2 Transit: Baltimore is not a very rail-oriented city. Perhaps this is a result of them being so close to the water. There is only one subway line, and most of the transit comes in the form of buses. There are multiple bus types: cityLink buses are high frequency, high traffic routes and are color coded. localLink routes have stops closer together and are numbered, connecting the tangential segments of the city, whereas the cityLink buses are the radial segments [think of it like a giant polar coordinate system, where cityLink buses operate in the $\vec r$ direction, while localLink buses operate in the $\vec \theta$ direction]. There are also free buses called Charm City Circulators, which have their own color coding system. Buses are harder for visitors to ride because you need to know where to get off using the pull cord/stop request. However, with tools like Google Maps, you just have to be very observant and things will be just fine. 
            \2 Climate: It was very cold this morning, but it warmed up significantly throughout the morning and early afternoon. Honestly, the weather was kinda beautiful - blue skies, very few clouds. 
            \2 Perceptions of the city's planning: Honestly it didn't seem too bad. Pedestrian infrastructure exists, and even outside of the central business district, there wasn't ever really an unsafe feeling. 
            \2 External POVs:
        \1 Other information 
            \2 Historical context: I don't know much about Baltimore other than the fact that it's a port city, and as a result, there was likely a lot of trade. Also the fact that it's on the East Coast in the mid-Atlantic region gives the impression of greater equity than in other places. 
            \2 Additional notes 
    \end{outline}
    \subsection{Washington, D.C.}
    \begin{outline}
    \1 Basics
        \2 When - In the afternoon after I was in Baltimore. I have also gone on other occasions with family and friends. 
        \2 Who - myself (this time)
        \2 Why - I thought that since I was in the area, I might as well visit since I haven't gone in a while and it would be a fun way to broaden my horizons and ride MARC. 
        \2 What - Walked the entire length of the Mall, visited the Air and Space Museum, had dinner out of a food truck (kinda embarassing ik). 
        \2 Where - I stayed on the Mall except when I had to go back to Union Station, when I walked through parts of the city (and GW University!)
    \1 Impressions
        \2 People - I didn't interact with that many people. Most people there were tourists, but given the circumstances with COVID and the time of day, they were probably mostly Americans. The locals that I saw were indicated by the fact that they were walking pets or exercising. 
        \2 Transit - I went right in the middle of DC's issues with the Metro derailments. As a result, trains were running less than usual and I had to walk a much longer distance to a Red Line station so I could avoid having to transfer and potentially missing my train back to Baltimore. 
        \2 Climate - It was hoodie weather. It did get kinda cold in the early evening though when I was trying to eat outside. 
        \2 Other notes - Obviously I didn't see any of the inner city or places where actual people from DC live, so the DC people experience as tourists is completely different than the one people who have lived there their whole life do. 
    \end{outline}
    \subsection{Chicago}
    \begin{outline}
        \1 Basics 
            \2 When - during the summer 2021 (wanna say August)
            \2 Who - myself 
            \2 Why - college visits, also I'd never been to Chicago before so this was super exciting!
            \2 What - Visited Northwestern, saw a lot of the skyline, visited IIT, walked through UChicago, visited MDW to talk to a flight instructor. Spent a lot of time on trains lol. 
            \2 Where - I walked around on the near south side (IIT), a little farther south near UChicago, also saw Lincoln Park, and the area around MDW. 
        \1 Impressions
            \2 People - mostly pretty nice and reasonable. Chicago is extremely diverse. 
            \2 Transit - one of the best systems in the US. Very robust, reliable, gets you where you need. 
            \2 Climate - the weather was lovely during the summer. I'm visiting again in February - let's see how the weather is then. 
            \2 Other - Going around the South Side was very eye-opening. It seemed rather rundown in a lot of places. On the north side, the walkability was reduced, and you notice that it is once-again car focused infrastructure. 
    \end{outline}
    *TBC*
    % \subsection{Cleveland}
    % \begin{outline}
    %     
    % \end{outline}
    % \subsection{Boston}
    % \begin{outline}
    %     
    % \end{outline}
    % \subsection{New York}
    % \begin{outline}
    %     
    % \end{outline}
    % \subsection{San Francisco}
    % \begin{outline}
    %     
    % \end{outline}
    % \subsection{Beijing}
    % \begin{outline}
    %     
    % \end{outline}
    % \subsection{Yantai}
    % \begin{outline}
% 
    % \end{outline}
    % \subsection{Philadelphia}
    % \begin{outline}
% 
    % \end{outline}
    % \subsection{New Haven}
    % \begin{outline}
% 
    % \end{outline}
    % \subsection{Pittsburgh}
    % \begin{outline}
% 
    % \end{outline}
    % \subsection{Toronto}
    % \begin{outline}
% 
    % \end{outline}
    % \subsection{Montreal}
    % \begin{outline}
% 
    % \end{outline}
    % \subsection{Quebec City}
    % \begin{outline}
% 
    % \end{outline}
    % \subsection{Houston}
    % \begin{outline}
% 
    % \end{outline}
\end{document}